An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures

### 2021-04-23 CMPSpaper_writing/CMPSpaper_writing.Rmd
code and figure side by side. Still need to get rid of the ```=latex

---
title: An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures
header-includes:
  - \usepackage{xcolor}
  - \usepackage{longtable}
author:
  # see ?rjournal_article for more information
  - name: Will W. Ju
    affiliation: Department of Statistics
    address:
    - Center for Statistics and Applications in Forensic Evidence
    - Iowa State University
    - 2438 Osborn Dr
    - Ames, IA 50011
    url: https://github.com/willju-wangqian
    orcid: 0000-0002-9079-593X
    email:  wju@iastate.edu
  - name: Heike Hofmann
    url: https://github.com/heike
    email: hofmann@iastate.edu
    orcid: 0000-0002-9079-593X
    affiliation: Department of Statistics
    address:
    - Center for Statistics and Applications in Forensic Evidence
    - Iowa State University
    - 2438 Osborn Dr
    - Ames, IA 50011
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble

@@

```{r, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "\\textwidth",
  fig.align = "center"
)
```

@@

<!--
```{r, eval=FALSE}
sig.plot$segment_shift_plot
```
-->
```{r sigplot, echo=TRUE,  out.width="300px", fig.cap=" \\hh{I don't think we need fig 3 when we have fig 4 XXX} The dark grey line shows the comparison signature; each red line segment shows one comgruent matching profile segment. "}
sig.plot <- cmps_signature_plot(cmps_with_multi_scale)
sig.plot$segment_shift_plot
#knitr::include_graphics("img/sigplot1.png", dpi = 100)
```

The second element is called `signature_shift_plot`. On this visual both the reference signature and the comparison signature are plotted. The reference signature is aligned with the comparison signature based on the congruent registration position. And the congruent matching profile segments are highlighted.

@@

```{r, echo=TRUE, eval=TRUE,  out.width="300px", fig.cap="  \\hh{ Could you make the cnsidered segments visible, maybe by zebra-striped rectangles in the background? XXX} The dark grey line shows the comparison signature; the red line shows the reference signature. Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position. "}
sig.plot$signature_shift_plot
#knitr::include_graphics("img/sigplot2.png", dpi = 100)
```

>>>>

---
title: An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures
header-includes:
  - \usepackage{xcolor}
  - \usepackage{longtable}
  - \usepackage{adjustbox}            
  - \usepackage[font=small,skip=5pt]{caption}
  - \usepackage{subcaption}
  - \usepackage{afterpage}
author:
  # see ?rjournal_article for more information
  - name: Will W. Ju
    affiliation: Department of Statistics
    address:
    - Center for Statistics and Applications in Forensic Evidence
    - Iowa State University
    - 2438 Osborn Dr
    - Ames, IA 50011
    url: https://github.com/willju-wangqian
    orcid: 0000-0002-9079-593X
    email:  wju@iastate.edu
  - name: Heike Hofmann
    url: https://github.com/heike
    email: hofmann@iastate.edu
    orcid: 0000-0002-9079-593X
    affiliation: Department of Statistics
    address:
    - Center for Statistics and Applications in Forensic Evidence
    - Iowa State University
    - 2438 Osborn Dr
    - Ames, IA 50011
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble

@@

```{r, echo=FALSE}
library(knitr)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "\\textwidth",
  fig.align = "center"
)
```

```{r setup_knitr, echo=FALSE}
## From Josh O'Brien's stackoverflow answer:
## http://stackoverflow.com/questions/11030898/knitr-how-to-align-code-and-plot-side-by-side
## These two settings control text width in codefig vs. usual code blocks
partWidth <- 35
fullWidth <- 60
options(width = fullWidth)

##  (1) CHUNK HOOK FUNCTION
##   First, to set R's textual output width on a per-chunk basis, we
## need to define a hook function which temporarily resets global R's
## option() settings, just for the current chunk
knit_hooks$set(r.opts = local({
    ropts <- NA
    function(before, options, envir) {
        if (before) {
            ropts <<- options(options$r.opts)
        } else {
            options(ropts)
        }
    }
}))

## (2) OUTPUT HOOK FUNCTION

##   Define a custom output hook function. This function processes _all_
## evaluated chunks, but will return the same output as the usual one,
## UNLESS a 'codefig' argument appeared in the chunk's header.  In that
## case, wrap the usual textual output in LaTeX code placing it in a
## narrower adjustbox environment and setting the graphics that it
## produced in another box beside it.

defaultChunkHook <- environment(knit_hooks[["get"]])$defaults$chunk

codefigChunkHook <- function(x, options) {
  main <-  defaultChunkHook(x, options)
  before <-
    "\\vspace{1em}
\\begin{adjustbox}{valign=t}
\\begin{minipage}{.49\\textwidth}\n"
  after <-
    paste("\\vspace{1em}
\\end{minipage}
\\begin{minipage}{.49\\textwidth}",
    paste0("\\includegraphics[width=\\textwidth]{CMPSpaper_writing_files/figure-latex/",
                 options[["label"]], "-1.pdf}
\\end{minipage}
\\end{adjustbox}"),
          sep = "\n")
  ## Was a codefig option supplied in chunk header?
  ## If so, wrap code block and graphical output with needed LaTeX code.
  if (!is.null(options$codefig)) {
    return(sprintf("%s%s\n%s", before, main, after))
  } else {
    return(main)
  }
}

knit_hooks[["set"]](chunk = codefigChunkHook)

## (3) TEMPLATE
##   codefig=TRUE is just one of several options needed for the
## side-by-side code block and a figure to come out right. Rather
## than typing out each of them in every single chunk header, we
## define a _template_ which bundles them all together. Then we can
## set all of those options simply by typing opts.label="codefig".

opts_template[["set"]](
codefig = list(codefig = TRUE, fig.show = "hide",
               r.opts = list(width = partWidth),
               tidy.opts = list(width.cutoff = partWidth)))
```

@@

\begin{figure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot}The dark grey line shows the comparison signature; each red line segment shows one congruent matching profile segment.}
```{r sigplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
sig.plot <- cmps_signature_plot(
  cmps_with_multi_scale
)
sig.plot$segment_shift_plot
```
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot2}The dark grey line shows the comparison signature; the red line shows the reference signature. Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
```{r sigplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
sig.plot$signature_shift_plot
```
\end{subfigure}
\caption{\label{sigplots}\hh{The resulting two figures signature plots. We need a summarizing sentence here.}}
\end{figure}

The second element is called `signature_shift_plot`. \hh{It is shown in \autoref{fig:sigplot2}.} On this visual both the reference signature and the comparison signature are plotted. The reference signature is aligned with the comparison signature based on the congruent registration position. And the congruent matching profile segments are highlighted.

@@
